---
title: "wartezeit_p4"
format: html
editor: visual
---

## Peter's R - Solving prolonged waiting-times with tidymodels

### part 4

Script for this medium blog
https://kphahn57.medium.com/peters-r-solving-prolonged-waiting-times-with-tidymodels-p4-242724e0dac7


### Load the preprocessed data

### load data from my repository https://github.com/phahn57/medium_wz

For this part you need wait_2.csv which contains additional text information.

### modify the directory in the read_csv

```{r}
#| label: load-packages
#| include: false
library(tidyverse)
library(tidytext)
library(tidymodels)
library(janitor)
library(doMC)
library(textrecipes)
library(embed)

### Load the preprocessed data
### load data from my repository https://github.com/phahn57/medium_wz
wait <- read_csv("../data/wait_2.csv")
### Variables used
### Load the preprocessed data
```

### Use subset of available data

#### remove numbers

```{r}
ml_fall <- wait %>% mutate(bez = str_c(op_kenn, bez, sep = " ")) %>%
        mutate(bez = str_remove_all(bez,"[0-9]")) %>%
        mutate(bez = str_remove_all(bez,"\\(|\\)|\\:|\\.")) %>%
        filter(p2p - sn_zeit < 40) ## ungewöhnlich hohe Differenz !

ml_fall <- ml_fall %>% select(age, p2p, wtag, arzt_code, stat, bez)
```

### Split data and build folds

```{r}
set.seed(1234)
fall_split <- ml_fall %>%
  initial_split(strata = p2p) 
hc_train <- training(fall_split)
hc_test <- testing(fall_split)

hc_fold <- vfold_cv(hc_train, v = 10)
rm(ml_fall)
```

```{r}
basic_rec <- 
    recipe(p2p ~ ., data = hc_train) %>%
        step_tokenize(bez)  %>%
        step_stopwords(bez, language = "de") %>%
        step_tokenfilter(bez, max_tokens = tune()) %>%
        step_tf(bez) %>% 
        #step_lencode_glm(op_kenn, outcome =vars(p2p)) %>% 
        step_dummy(all_nominal(), -all_outcomes()) %>%
        step_zv()

```

```{r}
library(rules)
library(baguette)
xgb_spec <- 
   boost_tree(tree_depth = tune(),learn_rate = tune(), loss_reduction = tune(), 
              min_n = tune(), sample_size = tune(), trees = tune()) %>%  
   set_engine("xgboost") %>% 
   set_mode("regression")

xgb_wf <- 
        workflow() %>% 
        add_recipe(basic_rec) %>% 
        add_model(xgb_spec)
xgb_wf
```

```{r}
library(finetune)

xgb_param <- extract_parameter_set_dials(xgb_wf)

registerDoMC(cores = 6)
multi_metric <- metric_set(rmse)

set.seed(1308)
xgb_race <-
  xgb_wf %>%
  tune_race_anova(
    hc_fold,
    grid = 20,
    param_info = xgb_param,
    metrics = multi_metric,
    control = control_race(save_pred = TRUE, verbose_elim = TRUE)
  )

registerDoSEQ()
```

## Last_fit

Fit the best model to the training set and evaluate against the test set.

```{r}
best_results_all <- 
        xgb_race %>% 
        show_best(metric = "rmse")

best_results <- 
        xgb_race %>% 
        select_best(metric = "rmse")

boosting_test_results <- 
   xgb_wf %>% 
   finalize_workflow(best_results) %>% 
   last_fit(split = fall_split)

collect_metrics(boosting_test_results)
```

```{r}
boosting_test_results %>% 
   collect_predictions() %>% 
   ggplot(aes(x = p2p, y = .pred)) + 
   geom_abline(color = "gray50", lty = 2) + 
   geom_point(alpha = 0.5) + 
   coord_obs_pred() + 
   labs(x = "observed", y = "p2p predicted")
```

### Importance

```{r}
library(vip)

final_wfl <- 
   xgb_wf %>% 
   finalize_workflow(best_results)

fitted_wfl <- final_wfl %>%  
        fit(data = hc_train) 

fitted_wfl %>%
  extract_fit_parsnip() %>%
  vip(geom = "point", num_features = 15)
```

```{r}
predict(fitted_wfl,hc_test[2,])
```

```{r}
saveRDS(wz_model, "../models/model1.RDS")
```

```{r}
mod1 <- readRDS("../models/model1.RDS")
```

```{r}
predict(mod1,hc_test[4,])
```
